Understanding the technological transition based on cultural transmission biases during the Late Pleistocene in Korea

### 2020-05-15 analysis/paper/paper.Rmd
deal with stringsAsFactors change for R 4.0.0

  for (i in 1:l) {
    landmarks[i] = list(data.frame(
      read.table(file = data, header = F, skip = LM[i],
                 nrows = nrows[i], col.names = c("X", "Y")),
      IMAGE = as.character(images[i]),
      ID = ID[i],
      SCALE = SCALE[i]))
  }
  do.call(rbind, landmarks) # rbind the list items into a data.frame
}

@@

Computing size attributes of the points by calculating distance between landmakrs
```{r}

>>>>

  for (i in 1:l) {
    landmarks[i] = list(data.frame(
      read.table(file = data, header = F, skip = LM[i],
                 nrows = nrows[i], 
                 col.names = c("X", "Y"),
                 stringsAsFactors = TRUE),
      IMAGE = as.character(images[i]),
      ID = ID[i],
      SCALE = SCALE[i],
      stringsAsFactors = TRUE))
  }
  do.call(rbind, landmarks) # rbind the list items into a data.frame
}

@@

Computing size attributes of the points by calculating distance between landmarks
```{r}
